---
title: "CHOW"
author: "Zoe Yang"
date: "15/03/2020"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
```

# Food filtering
```{r}
food <- read.csv("food.csv")
head(food)
```

# Assess fiber levels in menu items - right of red line indicates fiber levels >10g
```{r}
ggplot(food,aes(Fiber..g.))+geom_histogram(fill="#036635")+labs(x= 'Fiber',y = 'Count', title = paste("Distribution of Fiber")) +theme_classic()+geom_vline(xintercept = 10, linetype="dotted", color = "red", size=1.0)
```

# Assess carb levels in menu items - right of red line indicates carb levels greater than 60g
```{r}
ggplot(food,aes(Carb...g.))+geom_histogram(fill="#036635")+labs(x= 'Carb',y = 'Count', title = paste("Distribution of Carbs")) +theme_classic()+geom_vline(xintercept = 60, linetype="dotted", color = "red", size=1.0)
```


# Diabetic patients are recommended to eat between 25g-50g of fiber daily and 45g-75g of carbs per meal. Filter for menu items with >10g of fiber and 45g-75g of carbs
```{r}
diabetesfoods <- filter(food, Fiber..g.>10) %>% filter(between(Carb...g.,45,75))
head(diabetesfoods)
```

# Drinks filtering
```{r}
drinks <- read.csv("starbucks_drinkMenu_expanded.csv")
head(drinks)
summary(drinks)
```

# Asses sugar level - right of red line indicates sugar levels >35g
```{r}
ggplot(drinks,aes(Sugars..g.))+geom_histogram(fill="#036635")+labs(x= 'Sugars',y = 'Count', title = paste("Distribution of Sugars")) +theme_classic()+ geom_vline(xintercept = 35, linetype="dotted", color = "red", size=1.0)
```

# Asses protein level 
```{r}
ggplot(drinks,aes(Protein..g.))+geom_histogram(fill="#036635")+labs(x= 'Protein',y = 'Count', title = paste("Distribution of Protein")) +theme_classic()
```

# Filter for drinks with < 35g of sugar and >5g of protein
```{r}
diabetedrinks <- filter(drinks, Sugars..g. < 35) %>% filter(Protein..g. > 5)
head(diabetedrinks)
```

